Density dependence

### 2020-09-24 R/density dependence.Rmd
incorporated random effects into GAMs.

```{r}
m_surv <- glmer(surv ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number) + (1|year), 
                family = binomial, data = ha_sub)
```

@@

# Q_log <- log(Q+1)
g_growth <-
  gam(shts_next ~ s(log_shts) +
        habitat +
        s(Q, L,
          bs = "cb",
          # k = c(10, 10),
          xt = list(bs = "cr")),
      family = gaussian(link = "log"),
      data = ha_sub,
      method = "REML")
gam.check(g_growth)
anova(g_growth)
```

@@

```{r eval=FALSE}
g_surv <-
  gam(surv ~ s(log_shts, k = 12) +
        habitat +
        s(Q, L,
          bs = "cb",
          # k = c(10, 10),
          xt = list(bs = "cr")),
      family = binomial,
      data = ha_sub,
      method = "REML")
gam.check(g_surv)
anova(g_surv)
```
No significant effect of density

@@

```{r eval=FALSE}
hist(Q)
pred_growth <- crosspred("Q", model = g_growth, cumul = TRUE, cen = mean(Q, na.rm = T), from = 0, to = 8)
summary(pred_growth)
```

## Plot crossbasis

### Contour plot

@@

>>>>

```{r}
m_surv <- glmer(surv ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number) + (1|year_post), 
                family = binomial, data = ha_sub)
```

@@

# Q_log <- log(Q+1)
g_growth <-
  gam(shts_next ~ s(log_shts) +
        habitat +
        s(Q, L,
          bs = "cb",
          # k = c(10, 10),
          xt = list(bs = "cr")) +
        s(year_post, bs = "re"),
      family = gaussian(link = "log"),
      data = ha_sub,
      method = "REML")
gam.check(g_growth)
anova(g_growth)
```

@@

```{r eval=FALSE}
g_surv <-
  gam(surv ~ s(log_shts) +
        habitat +
        s(Q, L,
          bs = "cb",
          # k = c(10, 10),
          xt = list(bs = "cr")) +
        s(year_post, bs = "re"),
      family = binomial,
      data = ha_sub,
      method = "REML")
gam.check(g_surv)
anova(g_surv)
```
Marginally significant effect of density on survival

@@

Growth:
```{r eval=FALSE}
hist(Q)
pred_growth <- crosspred("Q", model = g_growth, cumul = TRUE, cen = mean(Q, na.rm = T), from = 0, to = 8)
pred_surv <- crosspred("Q", model = g_surv, cumul = TRUE, cen = mean(Q, na.rm = T), from = 0, to = 8)
# 
# summary(pred_growth)
```

## Plot Growth

@@

## Plot Survival

```{r}
plot.crosspred(pred_surv,
               ptype = "contour",
               xlab = "#shoots/m^2",
               ylab = "distance (m)",
               cumul = FALSE,
               main = "Relative to mean competition")
```
Postive density dependence that drops off steeply after 1m
